A Hitchhiker's Guide to Reproducible Research in R

### 2021-07-18 manuscript.Rmd
natural language -> verbal closes #162

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a priori planned analyses from those conducted unplanned and post hoc.
For an a priori planned analysis, preregistration should reduce "researcher degrees of freedom" therefore the number of decisions researcher can make that could unduly influence the results.
Preregistrations, however, have a problem.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration are comprehensive and specific enough is to use preregistration templates, like the ones supplied by [The Open Science Framework](https://osf.io/).
The structure these templates provides can more effectively reduce researchers degrees of freedom than an unstructured approach [@bakkerEnsuringQualitySpecificity2020].
But these templates can not remove researchers degrees of freedoms completely, because it is impossible to describe every detail of an analysis for all but the simplest analysis with natural language. # Hier vielleicht schon ein Beispiel?

Our proposed solution is simple: Instead of describing the analysis, you write the code to conduct the analysis before you gather data.
We term this approach of writing and publishing code before data collection *preregistration as code (PAC)*.
PAC has the potential to all but eliminate researchers degrees of freedom. # Den Satz verstehe ich nicht

@@

We believe, however, that combining ideas from reproducibility and preregistration can turn this "neat" idea into a tool with tangible benefits for the research community. # Sehr gut

@@

Writing a preregistration in form of a research article has the advantage that researchers already have great expertise in how to write a scientific manuscript.
It follows that for preregistration they should stick to widely accepted standards of scientific writing [e.g. @apa7].
We have already explained the need for reproducibility standards in the process of writing such manuscript and it is therefore only natural to extend these arguments to preregistration.

@@

We believe that pairing PAC with the here presented workflow offers five advantages over classical preregistration.
First, a PAC removes any ambiguity regarding the translation of an analysis plan into code. # I would remove the term "natural language" everywhere
Second, while being rigorous, it offers the flexibility to incorporate data-dependent decisions, formulated as code. # Every data-depended decision that can be preregistered can be formulated as code
Researchers can, for example, formulate conditions under which they prefer one analysis type over the other.
For example, if distributional assumptions are not met, the code may branch out to employ robust methods; or, an analysis may perform automated variable selection mechanisms before running the final model.
Third, a PAC is more comprehensive by design because its completeness can be empirically checked with simulated data.
We believe it is easier with PAC to detect missing steps or ambiguous decisions.
Because of its strict structure, PAC can therefore more effectively minimize researchers degrees of freedom than a standard preregistration [@bakkerEnsuringQualitySpecificity2020].
Fourth, deviations from the preregistration are visible because they are reflected in changes to the code, which are managed and tracked with version control.
Fifth, the preregistration is merely a development stage of the final manuscript, thus sparing authors from writing and editors and reviewers from evaluating two separate documents.

@@

# everything that is written here should be sorted under the specific point
The introduction and theoretical background provide the basis for the studies' design.
We argue that researchers can plan more effectively if they formulate the planned analysis as a method section that again follows best practices for describing empirical research.
To ensure that the analysis is technically feasible, they can translate their method section into executable computer code for the data analysis using simulated data.
The researchers can include a temporary "faked" results section based on the simulated data, employing dynamic document generation.
This allows for an initial check whether the analysis actually runs without failure and helps to see whether the planned reporting (e.g., the selected statistics, figures, and tables) provides sufficient detail.

>>>>

Defining the research questions and planning data analysis before observing the research outcomes is called preregistration [@NosekRevolution2018].
Preregistration increases the credibility of empirical results by separating a priori planned analyses from those conducted unplanned and post hoc.
For an a priori planned analysis, preregistration should reduce "researcher degrees of freedom" therefore the number of decisions researcher can make that could unduly influence the results.
Preregistrations, however, have a problem.
Even when several researchers describe their analysis with the same terms, use the same data, and investigate the same hypothesis the results vary considerably [@silberzahnManyAnalystsOne2018].
The current best practice to ensure that the preregistration are comprehensive and specific enough is to use preregistration templates, like the ones supplied by [The Open Science Framework](https://osf.io/).
The structure these templates provides can more effectively reduce researchers degrees of freedom than an unstructured approach [@bakkerEnsuringQualitySpecificity2020].
But these templates can not remove researchers degrees of freedoms completely, because it is impossible to verbally describe every detail of an analysis for all but the simplest analysis.

Our proposed solution is simple:
Instead of describing the analysis, you write the code to conduct the analysis before you gather data.
We term this approach of writing and publishing code before data collection *preregistration as code (PAC)*.
PAC has the potential to all but eliminate researchers degrees of freedom that standard preregistration afford.

@@

We believe, however, that combining ideas from reproducibility and preregistration can turn this "neat" idea into a tool with tangible benefits for the research community.

@@

Writing a preregistration in form of a research article has the advantage that researchers already have great expertise in how to write a scientific manuscript.
It follows that for preregistrations they should stick to widely accepted standards of scientific writing [e.g. @apa7].
We have already explained the need for reproducibility standards in the process of writing such manuscript and it is therefore only natural to extend these arguments to preregistration.

@@

We believe that pairing PAC with the here presented workflow offers five advantages over classical preregistration.
First, a PAC removes any ambiguity regarding the translation of an verbal analysis plan into code.
Second, while being rigorous, it offers the flexibility to incorporate data-dependent decisions if they can be formulated as code.
Researchers can, for example, formulate conditions under which they prefer one analysis type over the other.
For example, if distributional assumptions are not met, the code may branch out to employ robust methods; or, an analysis may perform automated variable selection mechanisms before running the final model.
Third, a PAC is more comprehensive by design because its completeness can be empirically checked with simulated data.
We believe it is easier with PAC to detect missing steps or ambiguous decisions.
Because of its strict structure, PAC can therefore more effectively minimize researchers degrees of freedom than a standard preregistration [@bakkerEnsuringQualitySpecificity2020].
Fourth, deviations from the preregistration are visible because they are reflected in changes to the code, which are managed and tracked with version control.
Fifth, the preregistration is merely a development stage of the final manuscript, thus sparing authors from writing and editors and reviewers from evaluating two separate documents.

@@

The introduction and theoretical background provide the basis for the studies' design.
We argue that researchers can plan more effectively if they formulate the planned analysis as a method section that again follows best practices for describing empirical research.
To ensure that the analysis is technically feasible, they can translate their method section into executable computer code for the data analysis using simulated data.
The researchers can include a temporary "faked" results section based on the simulated data, employing dynamic document generation.
This allows for an initial check whether the analysis actually runs without failure and helps to see whether the planned reporting (e.g., the selected statistics, figures, and tables) provides sufficient detail.
